#Script parts on irregularity need to be adapted based on each country's reality as the documents for regularization are different in each country


```{r setup, fig.height=3, fig.width=7.5, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	collapse = FALSE,
	comment = NA,
	prompt = FALSE,
	results = "asis")

```

```{r cars2, include=FALSE}

library(tidyverse)
library(ggalluvial)
library(scales)
library(glue)
library(here)
library(sf)
library(summarytools)
library(leaflet)
library(gtsummary)
library(cowplot)
library(data.table)
library(ggplot2)
library(writexl)
library(haven)
library(tidyverse)
library(readxl)
library(srvyr)
library(robotoolbox)
library(labelled)
library(remotes)
library(dm)
library(janitor)
library(visdat)
library(dplyr)


```

```{r cars3, include=FALSE}

main_merged <- left_join(ind, main, by = c("_parent_index"="_index")) %>%
  rename(id_hogar = "_parent_index")%>%
  rename(id_individual = "_index")%>%
  filter(# eligibility criterias for survey
    DEMO_00.6 != "no",
    DEMO_5 != "no",
    DEMO_7 != "return_venezuela",
    DEMO_7 != "move_different_country") %>%
  mutate(    
    FS_D1_Q1 = as.numeric(as.character(FS_D1_Q1)),
    FS_D1_Q2 = as.numeric(as.character(FS_D1_Q2)),
    FS_D1_Q3 = as.numeric(as.character(FS_D1_Q3)),
    FS_D1_Q4 = as.numeric(as.character(FS_D1_Q4)),
    FS_D1_Q5 = as.numeric(as.character(FS_D1_Q5)),
    FS_D1_Q8 = as.numeric(as.character(FS_D1_Q8)),
    FS_D1_Q9 = as.numeric(as.character(FS_D1_Q9)),
    FS_D1_Q10 = as.numeric(as.character(FS_D1_Q10)),
    FS_D2_Q1 = as.numeric(as.character(FS_D2_Q1)),
    FS_D2_Q2 = as.numeric(as.character(FS_D2_Q2)),
    FS_D2_Q3 = as.numeric(as.character(FS_D2_Q3)),
    FS_D2_Q4 = as.numeric(as.character(FS_D2_Q4)),
    FS_D2_Q5 = as.numeric(as.character(FS_D1_Q5))
  )


main <- main %>%
  rename(id_hogar = "_index")


```

#database with responses of individuals from the household = ind
#database with responses of the head of household = main

#In destination
#Education - Costa Rica
```{r edu_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>%
  mutate(age1_rounded = floor(age1)) %>%
  mutate(child_edu = case_when(
    age1_rounded >= 5 & age1_rounded < 18 ~ "Yes",
    TRUE ~ "No"
  )) %>%
  filter(child_edu == "Yes") %>%
  count(EDU_D1_Q1=="no") %>% 
  mutate(percent = n / sum(n) * 100)

# View the frequency table
freq_table

```

#Education - Costa Rica
```{r edu_d2_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
    mutate(age1_rounded = floor(age1)) %>%
    filter(age1_rounded <= 3) %>%
    mutate(
        EDU_D2_Q1_no = coalesce(EDU_D1_Q1 == "no", FALSE),
        EDU_D2_Q2_not_in_hh_parents = coalesce(EDU_D2_Q2 != "in_hh_parents", FALSE)
    ) %>%
    count(EDU_D2 = EDU_D2_Q1_no & EDU_D2_Q2_not_in_hh_parents) %>%
    mutate(percent = n / sum(n) * 100)

freq_table

```

#Education - Costa Rica
```{r edu_d3_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
      mutate(age1_rounded = floor(age1)) %>%
    filter(age1_rounded >= 5 & age1_rounded < 18) %>%
  count(EDU_D1_Q1=="yes" & EDU_D3_Q1 < 5)%>%
  mutate(percent = n / sum(n) * 100)

freq_table

```

#Child Protection - Costa Rica
```{r cp_d1_costa_rica_new, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

ind_cp_d1 <- ind %>%
  rename(id_hogar = "_parent_index") %>%
  mutate(age1_rounded = floor(age1)) %>%
  group_by(id_hogar) %>%
  mutate(
    irregular_child = case_when(
      any(
        age1_rounded < 18 & (
          coalesce(MH_6_identification_document_destination, 0) != 1 &
          coalesce(MH_6_permission_destination, 0) != 1 &
          coalesce(MH_6_temporal_residency_destination, 0) != 1 &
          coalesce(MH_6_temporal_protection_destination, 0) != 1 &
          coalesce(MH_6_citizenship_destination, 0) != 1 &
          coalesce(MH_6_asylum_seeker_documents, 0) != 1
        )
      ) ~ 1,  # Set to 1 if all document fields are not 1 (meaning no documents are present)
      TRUE ~ 0  # Set to 0 if all children have at least one document
    )
  ) %>%
  ungroup()%>%
  select(id_hogar, irregular_child)
# Now perform the join and subsequent operations
main_merged_2 <- main %>%
  rename(id_hogar = "_index") %>%
  left_join(ind_cp_d1, by = "id_hogar") %>%
  group_by(id_hogar) %>%
  slice_head(n = 1) %>%  # Selects the first row of each group
  ungroup() 
 # Calculate frequency table
  freq_table <- main_merged_2%>%
  count(IND_PRO_CP_max = case_when(
    CP_D1_Q1 != "none" | irregular_child == 1 ~ 1,
    TRUE ~ 0
  )) %>%
  mutate(percent = n / sum(n) * 100)

freq_table

```


#Child Protection old - Costa Rica

```{r cp_d1_old_Costa_Rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(
    indicator = case_when(
      CP_D1_Q1 != "none"  ~ 1,
      TRUE ~ 0
    )
  ) %>%
  count(indicator) %>%
  mutate(percent = n / sum(n) * 100)

freq_table

```


#Health - Costa Rica

```{r he_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>% 
  count(HE_D1_Q1 == "yes" &HE_D1_Q2 == "no")%>%
  mutate(percent = n / sum(n) * 100)

freq_table


```

#Health - Costa Rica

```{r he_d2_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>% 
   filter(age1>=15 & INT_D1_Q1=="work")%>% 
  count(INT_D2_Q2 == "yes")%>%
  mutate(percent = n / sum(n) * 100)

freq_table

```


#Human Trafficking and Smuggling - Costa Rica

```{r hts_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  count(HTS_D1_Q1 == "yes" | HTS_D1_Q2 == "yes")%>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Human Trafficking and Smuggling - Costa Rica

```{r hts_d2_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  count(HTS_D2_Q1 != "none" & HTS_D2_Q1 != "not_applicable" )%>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Human Trafficking and Smuggling - Costa Rica

```{r hts_d2_irregularity_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>%
  group_by(id_hogar) %>%
  mutate(
    irregular_person = case_when(
      any(
        coalesce(MH_6_identification_document_destination, 0) != 1 &
        coalesce(MH_6_permission_destination, 0) != 1 &
        coalesce(MH_6_temporal_residency_destination, 0) != 1 &
        coalesce(MH_6_temporal_protection_destination, 0) != 1 &
        coalesce(MH_6_citizenship_destination, 0) != 1 &
        coalesce(MH_6_asylum_seeker_documents, 0) != 1
      ) ~ 1,  # Set to 1 if all document fields are not 1 (meaning no documents are present)
      TRUE ~ 0  # Set to 0 if all have at least one document
    ),
    HTS_D2_Q1_valid = HTS_D2_Q1 != "none" & HTS_D2_Q1 != "not_applicable" & irregular_person == 1
  ) %>%
  ungroup() %>%
  count(HTS_D2_Q1_valid) %>%
  mutate(percent = n / sum(n) * 100)

freq_table


```

#Human Trafficking and Smuggling - Costa Rica

```{r hts_d2_informality_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>%
  group_by(id_hogar) %>%
  mutate(
    any_member_informality = if_else(
      any(
        age1 >= 15 & (INT_D1_Q1 == "finding_work" | INT_D1_Q1 == "work") &
        (INT_D2_Q1 == "no" | INT_D2_Q2 == "no" | INT_D2_Q3 == "no"),
        na.rm = TRUE
      ),
      1, # Set to 1 if any condition is true
      0  # Set to 0 if none of the conditions are true
    ),
    HTS_D2_Q1_valid = HTS_D2_Q1 != "none" & HTS_D2_Q1 != "not_applicable" & any_member_informality == 1
  ) %>%
  ungroup() %>%
  count(HTS_D2_Q1_valid) %>%
  mutate(percent = n / sum(n) * 100)

freq_table

```

#Humanitarian Transportation - Costa Rica

```{r ht_d1_costa_rica_old, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
  count((HT_D1_Q1_walking == 1 |
           HT_D1_Q1_bike == 1) & HT_D1_Q2 == "30m-plus")%>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Humanitarian Transportation - Costa Rica

```{r ht_d1_costa_rica_new, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
  count(IND_HT_max = case_when(
    ((HT_D1_Q1_walking == 1 | HT_D1_Q1_bike == 1) & HT_D1_Q2 == "30m-plus") |
    HT_D1_Q1_informal_particular_transport == 1 |
    HT_D1_Q1_govt_ngo_transport == 1 |
    HT_D1_Q1_autostop == 1 ~ 1,
    TRUE ~ 0
  )) %>%
  mutate(percent = n / sum(n) * 100)

freq_table

```

#Integration - Costa Rica

```{r ind_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>% 
  filter(age1>=15 & (INT_D1_Q1 =="finding_work"|INT_D1_Q1=="work")) %>% 
  count(INT_D1_Q1 == "finding_work" )%>% 
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Discrimination  by Nationality - Costa Rica

```{r ind_d2_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>% 
  count(INT_D3_Q1_nationality == 1 )%>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Informal work - Costa Rica

```{r ind_d3_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
  mutate(INT_D2_Q3=INT_D2_Q2)%>% 
    mutate(age1_rounded = floor(age1)) %>%
  filter(age1_rounded>=15 & INT_D1_Q1 == "work") %>% 
  count(INT_D2_Q1 == "no"|INT_D2_Q2 == "no" | INT_D2_Q3 == "no")%>% 
  mutate(percent = n / sum(n) * 100)

freq_table
```

# Discriminated by Nationality in Workplace - Costa Rica

```{r ind_d3_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

library(dplyr)
library(tidyr)

freq_table <- main_merged %>% 
  mutate(
    condition = replace_na(
      (INT_D3_Q1 == "age" |
       INT_D3_Q1 == "sex" |  
       INT_D3_Q1 == "sexual_orientation" |
       INT_D3_Q1 == "gender_identity" |
       INT_D3_Q1 == "ethnics" |
       INT_D3_Q1 == "disability" |  
       INT_D3_Q1 == "nationality" |
       INT_D3_Q1 == "other") & INT_D3_Q2 == "work",
      FALSE
    )
  ) %>% 
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table

```

#Integration - Costa Rica

```{r ind_d4_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
  count(INT_D4_Q1 =="none")%>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Nutrition - Costa Rica

```{r nut_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
      mutate(age1_rounded = floor(age1)) %>%
  filter(MH_4=="women" & age1_rounded>14 & (NUT_D1_Q1 == "pregnant" | NUT_D1_Q1 == "breastfeeding"))%>%
  count(NUT_D1_Q2_nutritional_evaluation == 0 |
           NUT_D1_Q2_nutritional_counceling == 0 |
           NUT_D1_Q2_micronutrient_delivery == 0)%>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Nutrition - Costa Rica

```{r nut_d10_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
      mutate(age2_rounded = floor(age2)) %>%
 filter(age2_rounded >= 24 & age2_rounded < 59) %>%
  mutate(total = rowSums(select(., NUT_D10_Q1_breastmilk,
                                     NUT_D10_Q1_grains_roots,
                                     NUT_D10_Q1_legumes,
                                     NUT_D10_Q1_lacteo_products,
                                     NUT_D10_Q1_animal_protein,
                                     NUT_D10_Q1_eggs,
                                     NUT_D10_Q1_dark_leaf_vegetables,
                                     NUT_D10_Q1_other_vegetables,
                                     NUT_D10_Q1_other_fruits))) %>%
  count(total < 5)%>%
  mutate(percent = n / sum(n) * 100)
freq_table
```

#Nutrition - Costa Rica

```{r nut_d4_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
        mutate(age2_rounded = floor(age2)) %>%
  filter(age2_rounded <6)%>%
 count(NUT_D4_Q1_nutritional_evaluation == 0 |
        (NUT_D4_Q1_lactation_counseling == 0 | NUT_D4_Q1_non_lactation_counseling == 0))%>%
  mutate(percent = n / sum(n) * 100)
freq_table
```

#Nutrition - Costa Rica

```{r nut_d5_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
  mutate(age2_rounded = floor(age2)) %>%
  filter(age2_rounded <6)%>%
 count(NUT_D5_Q1 == "no")%>%
  mutate(percent = n / sum(n) * 100)
freq_table
```

#Nutrition - Costa Rica
```{r nut_d8_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- ind %>% 
    mutate(age2_rounded = floor(age2)) %>%
 filter(age2_rounded >= 24 & age2_rounded < 59) %>%
  mutate(condition = NUT_D8_Q1_nutritional_assessment_weight_height_arm_measurement == 0 |
                    (NUT_D8_Q1_counseling_support_breastfeeding_evaluation_positions_difficulties == 0 &
                     NUT_D8_Q1_counseling_support_non_breastfed_babies_formula_preparation_use_cleaning_feeding_utensils == 0) |
                    NUT_D8_Q1_counseling_trained_personnel_feeding_solid_foods_diversity_preparation_feeding_children == 0 |
                    NUT_D8_Q1_delivery_vitamin_mineral_supplements_iron_vitamin_a_powder_drops_syrups == 0) %>%
  count(condition)%>%
  mutate(percent = n / sum(n) * 100)
          
freq_table
```

#GBV -  Costa Rica

```{r gbv_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
 count(GBV_D1_Q1 == "yes")%>%
  mutate(percent = n / sum(n) * 100)
          
freq_table
```

# GBV - Costa Rica
```{r gbv_d3_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  count(condition = GBV_D3_Q1 %in% c(3, 4, 5)) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Protection - Costa Rica

```{r pro_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(condition = case_when(
    PROT_D1_Q1 != "none" ~ TRUE,
    TRUE ~ FALSE  # Set all other cases to FALSE
  )) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Protection - Costa Rica

```{r pro_d2_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
 count(PROT_D2_Q1 != "none")%>%
  mutate(percent = n / sum(n) * 100)
          
freq_table
```


#Protection - Costa Rica

```{r pro_d3_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
 count(PROT_D3_Q1 == "yes" & PROT_D3_Q3 == "no")%>%
  mutate(percent = n / sum(n) * 100)
          
freq_table
```

#Protection - Costa Rica

```{r pro_d4_Costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main_merged %>% 
  filter(MH_3 == "N-VE") %>%
  mutate(
    no_documents = case_when(
      coalesce(MH_6_identification_document_destination, 0) != 1 &
      coalesce(MH_6_permission_destination, 0) != 1 &
      coalesce(MH_6_temporal_residency_destination, 0) != 1 &
      coalesce(MH_6_temporal_protection_destination, 0) != 1 &
      coalesce(MH_6_citizenship_destination, 0) != 1 &
      coalesce(MH_6_asylum_seeker_documents, 0) != 1 ~ 1,  # Set to 1 if all document fields are not 1
      TRUE ~ 0  # Set to 0 if at least one document is present
    )
  ) %>%
  count(no_documents) %>%
  mutate(percent = n / sum(n) * 100)

freq_table

```

# Protection - Costa Rica

```{r pro_d5_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
  mutate(condition = case_when(
    (PROT_D5_Q1 == "yes" | PROT_D5_Q1 == "prefer_not_answer") &
    (PROT_D5_Q2_extortion == 1 |
     PROT_D5_Q2_general_violence == 1 |
     PROT_D5_Q2_afraid_armed_group == 1 |
     PROT_D5_Q2_health_risk == 1 |
     PROT_D5_Q2_insecurity == 1 |
     PROT_D5_Q2_persecuted_assaulted_discrim == 1) ~ TRUE,
    TRUE ~ FALSE  # Set all other cases to FALSE
  )) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Shelter - Costa Rica

```{r she_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>% 
  mutate(SHE_D1 = case_when(
      SHE_D1_Q1 == "street" |
      SHE_D1_Q1 == "shared_house" |
      SHE_D1_Q1 == "foster_family" |
      SHE_D1_Q1 == "rooming_house" |
      SHE_D1_Q1 == "hotel" |
      SHE_D1_Q1 == "shelters" |
      SHE_D1_Q1 == "colective" |
      SHE_D1_Q1 == "spontaneous" |
      SHE_D1_Q1 == "prefer_not_answer" |
      SHE_D1_Q2_house_unprotected_insecure == 1 |
      SHE_D1_Q2_neighboor_unprotected_insecure == 1 |
      SHE_D1_Q2_privacy == 1 |
      SHE_D1_Q2_natural_disasters == 1 |
      SHE_D1_Q2_wash_issues == 1 |
      SHE_D1_Q3_sewerage == 1 |
      SHE_D1_Q3_garbage_collection == 1 |
      SHE_D1_Q3_electricity == 1 |
      SHE_D1_Q3_acueduct == 1 ~ TRUE,
      TRUE ~ FALSE
    )) %>%
  count(SHE_D1)%>%
  mutate(percent = n / sum(n) * 100)
          
freq_table
```

#Shelter - Costa Rica

```{r she_d2_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
 filter(SHE_D1_Q1 != "street") %>%
  mutate(condition = (MH_1 / SHE_D2_Q1 > 3)) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Shelter - Costa Rica

```{r she_d3_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  filter(SHE_D1_Q1 != "street") %>%
  mutate(condition = case_when(
    SHE_D3_Q1_none == 0 ~ TRUE,
    TRUE ~ FALSE  # Set all other cases to FALSE
  )) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#Shelter - Costa Rica

```{r she_d4_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  filter(SHE_D1_Q1 != "street") %>%
  mutate(condition = SHE_D4_Q1 %in% c("some_eviction_risk", "evicted", "prefer_not_answer")) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#WASH - Costa Rica

```{r wa_d1_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(condition = (WASH_D1_Q1 %in% c("rain_water", "bottled_water", "water_supply", "water_kiosk", "unprotected_well_spring", "no_pump_well", "surface_water", "none") &
                      WASH_D1_Q2 == "30min_high")) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#WASH - Costa Rica

```{r wa_d2_costa_rica, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(condition = (WASH_D2_Q1 == "not_enough_water" |
                      !(WASH_D2_Q1 %in% c("drink", "cook", "hygiene", "other"))) &
                     (WASH_D2_Q2 %in% c("less_3days_week", "3days_week", "more3days_week", "restricted_schedule", "dont_know", "prefer_not_answer"))) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

# WASH - Costa Rica

```{r wa_d4_costa_rica fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(condition = case_when(
    WASH_D4_Q1 %in% c("improvised_latrine", "hanging_latrine", "no_sanitation_service_free_access", "no_sanitation_service_pay_access", "open_defecation") |
    WASH_D4_Q2 == "yes" ~ TRUE,
    TRUE ~ FALSE  # Set all other cases to FALSE
  )) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

# WASH - Costa Rica

```{r wa_d6_costa_rica fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(condition = case_when(
    WASH_D6_Q1 %in% c("river_stream", "patio_lot", "burnt", "dont_know") ~ TRUE,
    TRUE ~ FALSE  # Set all other cases to FALSE
  )) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#WASH - Costa Rica

```{r wa_d8 fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(condition = case_when(
    WASH_D8_Q1 %in% c("water", "soap", "cant_handwash", "antibacterial_gel") ~ TRUE,
    TRUE ~ FALSE  # Set all other cases to FALSE
  )) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```

#WASH - Costa Rica

```{r wa_d11_costa_rica fig.height=4, fig.width=7, message=FALSE, warning=FALSE, dev='svg', out.width='1000px'}

freq_table <- main %>%
  mutate(condition = case_when(
    WASH_D11_Q1 %in% c("no", "panty_liners", "cloth_fabric", 
                       "toilet_paper", "underwear_layers", 
                       "not_applicable", "other") ~ TRUE,
    TRUE ~ FALSE  # Set all other cases to FALSE
  )) %>%
  count(condition) %>%
  mutate(percent = n / sum(n) * 100)

freq_table
```


